Inquires in Racial and Sexual Disparities among Chicago Police Department

### 2024-02-15 paper/paper.qmd
Adding New regression figures and text

library(tidyverse)
library(tidyr)
library(janitor)
library(dplyr)
library(readr)
library(stringr)
library(stargazer)
```

@@

## Summary statistics.
```{r}
#| echo: false
# run code in ***name of script
organized_table_1 <- read.csv("~/Police-Award-Nomination-Paper-Reproduction/data/analysis_data/table_1_data.csv")
organized_table_1
```

@@

## Disparities in police awards 
```{r}
#| echo:  false
#| warning: false
#| message: false
 # run script **name

organized_table_2 <- read.csv("~/Police-Award-Nomination-Paper-Reproduction/data/analysis_data/table_2_data.csv")
organized_table_2

@@

>>>>

library(tidyverse)
library(tidyr)
library(janitor)
library(dplyr)
library(readr)
library(stringr)
library(stargazer)
library(kableExtra)
```

@@

## Summary statistics.
```{r}
#| label: tabl-one
#| echo: false
#| warning: false
#| message: false
# run code in ***name of script
organized_table_1 <- read.csv("~/Police-Award-Nomination-Paper-Reproduction/data/analysis_data/table_1_data.csv")

# stargazer(organized_table_1[,], type='latex')

kable(organized_table_1, "latex", booktabs = TRUE, caption = "Summary Statistics for My Data") %>%
  kable_styling(latex_options = c("striped", "hold_position"))
```

@@

## Disparities in police awards 
```{r}
#| label: tabl-two
#| echo:  false
#| warning: false
#| message: false
 # run script **name

organized_table_2 <- read.csv("~/Police-Award-Nomination-Paper-Reproduction/data/analysis_data/table_2_data.csv")

#kable(organized_table_2, "latex", booktabs = TRUE, caption = "Summary Statistics for My Data") %>%
#  kable_styling(latex_options = c("striped", "hold_position"))
organized_table_2

@@

```{r}
#| label: fig-one
#| echo: false
#| warning: false
#| message: false
C_df <- read.csv("~/Police-Award-Nomination-Paper-Reproduction/data/analysis_data/figure_1_data.csv")

ggplot(C_df, aes(x = qtile, y = coef, color = ifelse(bw == 1, "Black-White Gap", "Female-Male Gap"))) +
  geom_errorbar(aes(ymin = lb, ymax = ub), width = 0.02) +
  geom_point(size = 2, alpha=0.3) +
  ylab("Minority Gap") +
  xlab("Quantiles") +
  scale_x_continuous(breaks = seq(0.1, 0.9, by = 0.1)) +
  scale_color_manual(values = c("Black-White Gap" = "red", "Female-Male Gap" = "blue")) +
  theme_minimal() +
  theme(legend.position = "top", legend.title = element_blank())
```

```{r}
#| label: fig-two
#| echo: false
#| warning: false
#| message: false
#| 
officers = read.csv("~/Police-Award-Nomination-Paper-Reproduction/data/analysis_data/analysis_officer_year_data.csv")
black_officers = officers[officers$black == 1,]
white_officers = officers[officers$white == 1,]
black_officers$group <- "Black Officers"
white_officers$group <- "White Officers"

combined_data <- rbind(black_officers, white_officers)
ggplot(combined_data, aes(x = arrest_total, y = awd_perf, color = group)) +
  geom_point(alpha = 0.3) +  # Adjust alpha for transparency
  geom_smooth(method = "lm", se = FALSE) +  # Add lines of best fit
  labs(title = "Comparison of Arrest Total and AWD Performance",
       x = "Arrest Total",
       y = "Award Nominations") +
  scale_color_manual(values = c("Black Officers" = "red", "White Officers" = "blue")) +  # Set colors
  theme_minimal()

# Correlation for blakc officers: 0.601
# Correlation for white officers:0.53
```
```{r}
#| label: fig-three
#| echo: false
#| warning: false
#| message: false
male_officers = officers[officers$female == 0,]

female_officers = officers[officers$female == 1,]

male_officers$group <- "Male Officers"
female_officers$group <- "Female Officers"

combined_data <- rbind(male_officers, female_officers)
ggplot(combined_data, aes(x = arrest_total, y = awd_perf, color = group)) +
  geom_point(alpha = 0.3) +  # Adjust alpha for transparency
  geom_smooth(method = "lm", se = FALSE) +  # Add lines of best fit
  labs(title = "Comparison of Arrest Total and AWD Performance",
       x = "Arrest Total",
       y = "Award Nominations") +
  scale_color_manual(values = c("Male Officers" = "red", "Female Officers" = "blue")) +  # Set colors
  theme_minimal()

# Correlation for blakc officers: 0.611
# Correlation for white officers:0.520
```
